Towards a Machine Learning approach for Aggregate Computing

### 2021-10-06 paper-2021-woa-ac-ml.tex
more on the roadmap

\subsection{Roadmap}
\todo[inline, color=green]{AC + ML for building block refining -- offline}
\todo[inline, color=green]{AC + ML for building block refining -- online}
\todo[inline, color=green]{AC + ML for application refining -- offline/offline}
\todo[inline, color=green]{AC + ML for building block creation -- offline} %% why not?
\todo[inline, color=green]{AC + ML for building block creation -- online}
\todo[inline, color=green]{AC + ML for framework level -- online}

>>>>

\subsection{Roadmap}
The path towards a fully integration of Machine Learning and Aggregate Computing is long
 and probably we do not know the implications that it can bring. Currently, we program to:

\begin{enumerate}
  \item Enhance building block through learning -- \textbf{offline}: in this first step, we 
  need to understand what kind of learning mode is most suitable for us. To decrease the complexity,
  we aim at perform learning \textit{offline} and at the \textit{building block} level.
  \item Enhance building blocks through learning -- \textbf{online}: here, the most challenging part
  in bringing the offline results could be in the reward function definition. Indeed, at runtime
  we cannot use a global view of the system. Novel way in describe a collective reward by Aggregate Computing
  might be taken in consideration.
  \item Create building block through learning: some building block currenlty lack of a proper implementation -- 
  such the the distributed leader election -- so learning can help us also in crating them. 
  Here, though, the research space increase drastically, so possibility it cannot be easy to bring our 
  result there.
  \item Improve framework aspects through learning: when we successufly apply learning in the first two steps, 
  we can also consider to move learning at the framework level, to manage non-functional aspect. In this way,
  developers can really focus on the "high level" behaviour aspect.
\end{enumerate}
\todo[inline, color=green]{AC + ML for building block creation -- online}
\todo[inline, color=green]{AC + ML for framework level -- online}
